A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice

### 2020-01-28 0_reviewer_response.tex

The old photos (old Fig. 18, here \cref{prints_old}) of our print results already showed that adaptive width control is possible up to an admittedly insufficient extent.

Because it was insufficient, we have now developed a new method for actualizing adaptive width control which can readily be applied to unmodified FDM systems such as the Ultimaker S5: \emph{back pressure compensation}.
We show the results of back pressure compensation in a new figure (Fig. 15, reproduced here in \cref{back_pressure_compensation}) which clearly shows the achieved variance in bead width.

All paragraphs on the physical realization, i.e. on linear advance and its limitations and on gcode limitations, have been assembled together and moved to 5.1. Fabrication.
Because the print time statistics use our back pressure compensation approach we moved the fabrication results to before the statistical analysis.
}

\commits{
%3d7238e2787f17c4cff63804eb4b84439ff85f1b  % initial printing results section~5.2
%b5abdd980240cd4ca964ed0f4751c207baa09b85 % move 5.5 to 5.2
a0e98d1079b3ab3b262908ea056939813fc49c73 % move 5.2 to 5.3 and overhaul
6362bb7f1ff11e15efc6667fc7863ca12a29a8a9 % mention in intro and conclusion
22cb3664ddc722d25e0a73df905100410f8ebf10 444a00a54100e402024335b79265b6900017bc1d ab38e07c84b6e62dc028d224b7a57bba9239552f cb3325a9cf00457fab5f1bdc5d29f1d178de4e35% S5 prints
d375878a8a6d01c53436aeb9c473dbedd8f3edcf % prints discussion
125162ad9878c0fb5a054f1bab34aa7b1353b86c % better var width test figure
34e923fbf4c2ad45bf2dd0a03ef70d4a714b4b0b % lil comma (x2)
1b7bb61648b97b8084ca8817aa457bde2c91e1b3 % lil: explain unexplained math symbol 
}
\paper{Abstract}
{
We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices.}{layer outlines,}
\revise{}{and develop a technique for off-the-shelf FDM systems to effectively realize adaptive width called \emph{back pressure compensation}.}
}
\paper{5.1.2 Printing results}
{
\revisepar{
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs \emph{linear advance} for accurately realizing adaptive deposition width:
gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines narrower than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.
%}{}
\par
%\revisepar{
The prints are shown in \cref{prints_old}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
The prints which employ the uniform offsets technique show a lot of underfill, which impacts the visual quality of the print.
Moreover, in the case of the regular honeycomb there are several fully disconnected hexagons, which means the object falls apart.
The difference between the centered and the inward distributed schemes is less pronounced.
We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extreme bead widths.
The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
}{}

@@

We removed the angles graph of old Fig.~17e.
The effect that transitioning reduces sharp angles in the toolpath is apparent and doesn't require empirical proof.

We fixed a mistake when performing the statistical analysis. In the first submitted version we used a minimum bead width half of what it should have been for the centered scheme. The extrusion width statistics figure (now Fig.~18d, old Fig.~17b, \cref{widthHistogram} here) now shows little beads below \SI{0.2}{\milli\meter} instead of below \SI{0.1}{\milli\meter}.

We changed the width histogram calculation so that we use accurate statistics instead of sampling the width along the path.
\commits{d402ba3a47d35bc9a040b6ed4ccdfb85e911bedf}
\paper{5.2.2 Uniformity}
{
\revise{
We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
}{
We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
}
}

We have made some improvements on the abstract.
\commits{c5ecf8f8c5c15266059278a6b4c26774446e7854}
\paper{Abstract}{
Toolpath with uniform inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially problematic for thin parts such as casings and microstructures.
\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
 Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
 In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices.}{layer outlines,}
\revise{}{and develop a technique for off-the-shelf FDM systems to effectively realize adaptive width called \emph{back pressure compensation}.}
}

### 2020-01-28 0_main.tex
mention back pressure compensation in abstract

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices}{layer outlines}.
\end{abstract}

>>>>

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
\revise{By densely filling consecutive 2D layers with contour-parallel extrusion toolpaths, FDM can produce parts with high stiffness and strength.}
{High stiffness parts are produced by filling the 2D polygons of consecutive layers (partly) with contour-parallel extrusion toolpaths.}
\revise{Toolpath with uniform }{Toolpaths consisting of \emph{uniform}} inward offsets from the outline polygons produce over- and underfill regions in the center of the shape, which are especially \revise{problematic for }{detrimental to the mechanical performance of} thin parts such as casings and microstructures.
Existing approaches for generating toolpaths with adaptive width result in a large variation in widths, which for some hardware systems is difficult to realize accurately, if not beyond their capabilities.
In this paper we present a framework which supports multiple schemes to generate toolpaths with adaptive width, by using a function to decide the number of beads and their widths which are applied from the center outward.
Furthermore, we propose a novel scheme for FDM printing which \revise{avoids}{reduces} extreme bead width deviation\revise{ from the nozzle size}{}, \revise{and limits}{while limiting} the number of altered toolpaths.
We validate the effectiveness of our framework and this novel scheme on a data set of 300 \revise{slices.}{layer outlines,}
\revise{}{and develop a technique for off-the-shelf FDM systems to effectively realize adaptive width called \emph{back pressure compensation}.}
\end{abstract}
